---
title: "Mission Impossible 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import via a csv

Import the csv file called "mi2DataAll".

```{r}
library(readr)
gdp <- 
```

# Delete the column

Delete the column "X1".

```{r}
 
```

# Remove missing values

Remove all missing values from the dataframe "gdp".

```{r}
gdp2 <- 
```

# Gather the data

You need to gather (modify from wide to long) the dataframe "gdp2" to get three column: "country", "year", "gdp".

```{r}
library(tidyr)
gdp3 <- 
```

# Filter the data

Filter the data to only keep the following countries: "united states", "canada", "japan", "belgique", "FRA".

```{r}
library(dplyr)
gdp4 <- 
```

# Import via a gsheet 

Import the data containing the longitute and latitude from this gsheet : <https://docs.google.com/spreadsheets/d/1VUxLOL2GH2ULrZ-lqQUa5IPKeSH-4dy_hTevZUyqbv4/edit#gid=0>

```{r}
library(gsheet)
locations <- 
```

# Combining tables

Join the data frame "locations" to the data frame "gdp4". Before combining the data frames, make sure that all countries and columns have the same names!

```{r}
gdp5 <- 
```

# Delete a column

Delete the column "Continent".

```{r}

```

















